The Morality of Arbitrage - Some Half-Baked Ideas

### 2017-06-23 Slides/morality-slides.Rmd
Changes for the APEE presentation.
Updating with Lewis quotation.

---
title: "The Morality of Arbitrage - Some Half-Baked Ideas"
author: "Tyler J. Brough"
date: "September 23, 2016"
output: ioslides_presentation
---

@@

<div class="notes">
- Of course, all good ideas begin with Hayek!
</div>

>>>>

---
title: "The Morality of Arbitrage - Some Half-Baked Ideas"
author: "Tyler J. Brough"
date: "September 23, 2016"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

@@

<br>
<br>

> *The task of the modern educator is not to cut down jungles but to irriage deserts. The right defense against false
> sentiments is to inculcate just sentiments. By starving the sensibility of our pupils we only make them easier prey to
> the propagandist when he comes. For famished nature will be avenged and a hard heart is no infallible protection
> against a soft head.*

-- C.S. Lewis

<div class="notes">
- Of course, all good ideas begin with Hayek!
- And Lewis!
</div>
